---
output:
  md_document:
    variant: markdown_github
---
[![Build Status](https://travis-ci.org/jamesdunham/concatenate.svg?branch=master)](https://travis-ci.org/jamesdunham/concatenate)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/concatenate)](https://cran.r-project.org/package=concatenate)

Each function in concatenate returns a comma-separated string. (A length-one
character vector.) They can be used to construct human-friendly messages whose
elements aren't known in advance, like  calls to `message`, `warning` or `stop`,
from clean code.

## Basics

```{r, knitr-options, echo = FALSE}
# rmarkdown::render("README.Rmd")
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  cache = FALSE)
library(concatenate)
```

The workhorse function in concatenate is `cc`.
```{r}
cc("one fish", "two fish")
```

Its wrappers `cc_or` and `cc_and` insert "or" and "and" between the last two
elements of the input.
```{r}
cc_and("this", "that", "the other")
cc_or("one way", "another")
```

`cn` and its derivatives combine these functions with `sprintf`-like
substitution and the grammatical number awareness of `ngettext`.

```{r}
x <- unique(iris$Species)
cn_and(x, "a single species: %c", "%n unique species: %c")
```

There are row-wise `data.frame` methods for the `cn` functions.
```{r}
singular <- "%n row: %c"
plural <- "%n rows whose values are %c"
cn(chickwts[1, ], singular, plural)
cn_and(chickwts[1:3, 1, drop = FALSE], singular, plural)
```

The `cc` functions are also available as binary infix operators.
```{r}
x <- "important value"
x %+% "!"
```

## Install

concatenate is available
[via CRAN](https://cran.r-project.org/package=concatenate).
```
install.packages("concatenate")
```

Or, get it from GitHub.
```
devtools::install_github("jamesdunham/concatenate")
```
